\documentclass[11pt,a4paper,sans]{moderncv}

% Установка шрифтов
\usepackage[russian]{babel}
\usepackage{tabularx}

% Выбор стиля
\moderncvcolor{blue}    % Цвет темы (blue, orange, green, red, purple, etc.)
\moderncvstyle{banking} % Стиль (banking, classic, casual, etc.)
\colorlet{firstnamecolor}{lastnamecolor}

% Установки страницы
\usepackage[scale=0.75]{geometry}

% Личные данные
\name{Kirill}{Kozlov} 
\address{Moscow,Russia}
\phone[mobile]{+7 (910) 968 1153}
\email{kirillkozlov.yar@gmail.com}
\social[github]{noobmaster-ru}
\social[telegram]{@noobmaster\_rus}


% Начало документа
\begin{document}
\nopagenumbers{}

% Заголовок
\makecvtitle

% Раздел "Образование"
% \section{Education}
% \cventry{Aug 2022 - Present}{Faculty of Computional Mathematics and Cybernetics}{Moscow State University}{Moscow}{}{
% }

\section{Education}
\cventry{Aug 2022 -- Present}{Faculty of Computational Mathematics and Cybernetics}{Lomonosov Moscow State University}{Moscow}{}{}

% Раздел "Курсы"
% \section{Relevant Coursework}
% \cvitem{}{{\bfseries Deep Learning School (DLS)} --- MIPT School of Deep Learning}
\section{Relevant Coursework}
\cvitem{}{\textbullet\ \textbf{Deep Learning School (DLS)} --- MIPT School of Deep Learning}

% Раздел "Опыт работы"
\section{Work Experience}
\cventry{Apr 2026 -- Present}{ML Engineer}{X5 Tech (Russia's largest grocery retailer)}{Moscow}{}{
\begin{itemize}
    \item Developing a RAG system for legal document analysis to help X5 Group save up to RUB 19B annually.
\end{itemize}
}

% Раздел "Проекты"
\section{Projects}
\cventry{Jul 2024 -- Dec 2024}{Developer}{Placa}{Moscow}{}{
\begin{itemize}
    \item Built a Google Sheets analytics service for Wildberries sellers using Google Apps Script and Wildberries API integration.
    \item Implemented a self-service Google Sheets template: copy → paste token → click control-panel buttons → daily automatic data loading.
    \item The solution enables ~300 sellers to receive up-to-date advertising spend data on a daily basis.
\end{itemize}
}

\cventry{Jul 2025 -- Sep 2025}{Python Developer}{WB Parser / Telegram Mini App}{Moscow}{}{
\vspace{2pt}
\begin{itemize}
    \item Developed a Wildberries search parser with filtering by organic search position.
    \item Delivered the product as a Telegram Mini App with a database backend; reached 220 active users.
\end{itemize}
}

\cventry{Oct 2025 -- Apr 2026}{Python Developer}{\href{https://github.com/noobmaster-ru/axiomai}{AxiomAI}}{Moscow}{}{
\vspace{2pt}
\begin{itemize}
    \item Built and deployed a production Telegram bot with OpenAI API, Redis, and Docker.
    \item Improved response speed and reduced manual manager workload in business communications.
\end{itemize}
}

\section{Skills, Activities , Interests}
\noindent
\begin{tabularx}{\textwidth}{@{}l X@{}}
\textbf{Languages:}  Russian -- Native, English -- Upper-Intermediate \\
\textbf{Programming Languages:}  Python, Go, C++ \\
\textbf{Frameworks:}  FastAPI, aiogram, aiohttp, pytest, pytorch \\
\textbf{Developer Tools:} Git, Linux, Docker, CI/CD, Google Cloud Platform, VS Code, PostgreSQL, Redis\\
\textbf{Libraries:}  asyncio, requests, pandas, numpy, sklearn  \\
\textbf{Interests:}  Volleyball, Gym, Economy, History \\
\end{tabularx}

% Конец документа
\end{document}